---
title: "Week 4 Part 1 - CIs & t-tests"
author: "Katelyn Toigo"
date: "10/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. Confidence intervals

This is a one sample t-test but it used the default that the mean population length is 0 inches, which makes no sense.
```{r}
otter_length <- c(38, 41, 50, 67, 32, 47, 45, 65, 56)

t.test(otter_length)
```


## t-test (1-sample t-test)

If you go to the console and type in ?t.test it will show you how to code this function and the defaults.

When I type "otter_length <-" this means that the output will go onto a table in the environment table. If I want to see it on the markdown document, I need to call it.  Which means I type just the name "otter_test".

See a claim: mean otter length is 50 inches

```{r}
otter_test <- t.test(x=otter_length, mu = 50)
otter_test
```

## t-test (2-sample t-test)

confidence interval for difference of means is not often reported

```{r}
desert_bighorns <- c(32, 44, 18, 26, 50, 33, 42, 40)
sierra_bighorns <- c(28, 31, 40, 42, 26, 29, 31)

t.test(x = desert_bighorns, y = sierra_bighorns)
```
